Capabilities, MMIO and Robust Safety

### 2020-03-31 capability-meetings-notes/10-03/main.tex
MMIO notes; verbal description of semantic bootspec

>>>>

It should be noted that a more general, semantic version of this specification
is also possible. It would contain the following elements, that should all
follow directly from the specification above:
\begin{itemize}
\item All registers except \X{PC} are in the value relation with respect to
  either the empty world (if we do not want to allow any non-empty, non-enter
  capabilities in registers), or a world containing a single standard region for
  all of the adversary's memory.
  The \X{PC} register satisfies both the read- and write conditions (note the
  parallel with the fundamental theorem) with respect to this same world, if we
  picked the non-empty world, or just points to the adversary's memory, which
  does not contain capabilities (if we
  picked the empty world, a capability pointing into memory can never be valid).
  It feels slightly less artificial to pick the non-empty world option here.
\item We have possession of the predicates $\I{region}$ and
  $\I{sts\_full\_world}$ for the world we picked in the previous bullet. we will
  need these to apply the fundamental theorem.
\item A description of the exact driver code, still in terms of points-to chunks
  (or, in this case equivalently, an invariant)
\end{itemize}
